A meta-analysis of fungicide spray schedules to minimise yield loss from powdery mildew in Australian mungbean

### 2021-02-01 01_TrialsForInclusionInAnalysis.Rmd

### Summary of all trials  
```{r data_summary, echo=FALSE, message=FALSE, warning=FALSE}
PM_MB_dat %>%
   arrange(year, location) %>%
   group_by(trial_ref) %>%
   summarise(
         Year = unique(year),
         Location = unique(location),
         `Replicates per treatment` = if(all(replicates[1] == replicates)){
            as.character(replicates[1])}else{
               as.character(paste(min(replicates),"-",max(replicates)))},
         `Planting date` = unique(planting_date),
         `First sign of disease` = unique(first_sign_disease),
         `Fungicide treatments` = length(n_treatment),
      ) %>%
      arrange(Year)%>%
   kable(caption = "Description of Experiments",
         align = "c",
         col.names = c("Unique Trial\nReference","Year", "Location", "Replicates\nper treatments",
                       "Planting date", "First sign\nof disease", "Fungicide\n treatments")
         )  %>%
   kable_styling(fixed_thead = TRUE, full_width = TRUE) %>%
   column_spec(c(3,5:6), width = "3cm") %>% 
   scroll_box(height = "500px")

@@

The demethylation inhibitors (DMI), tebuconazole and propiconazole, are used in the highest frequencies.
Thee DMIs have the same fungicide mode of action and are good candidates to be pooled in the meta-analysis.

@@

Finally we are going to define the class of each variable in the data, retaining only the variables relevant to the analysis. 
It should be noted that the data-set below has still retained all fungicide active ingredients. 
Before dropping the non-DMI fungicides from the final meta-analysis we will inspect their influence on grain yield.

>>>>

### Summary of all trials  
```{r data_summary, echo=FALSE, message=FALSE, warning=FALSE}
PM_MB_dat %>%
   arrange(year, location) %>%
   group_by(trial_ref) %>%
   summarise(
      Year = unique(year),
      Location = unique(location),
      `Replicates per treatment` = if (all(replicates[1] == replicates)) {
         as.character(replicates[1])
      } else{
         as.character(paste(min(replicates), "-", max(replicates)))
      },
      `Planting date` = unique(planting_date),
      `First sign of disease` = unique(first_sign_disease),
      `Fungicide treatments` = length(n_treatment),
   ) %>%
   arrange(Year) %>%
   kable(
      caption = "Description of Experiments",
      align = "c",
      col.names = c(
         "Unique Trial\nReference",
         "Year",
         "Location",
         "Replicates\nper treatments",
         "Planting date",
         "First sign\nof disease",
         "Fungicide\n treatments"
      )
   )  %>%
   kable_styling(fixed_thead = TRUE, full_width = TRUE) %>%
   column_spec(c(3, 5:6), width = "3cm") %>%
   scroll_box(height = "500px") 
```

@@

The demethylation inhibitors (DMI), tebuconazole and propiconazole, are used in the highest frequencies.
The DMIs have the same fungicide mode of action and are good candidates to be pooled in the meta-analysis.

@@

Finally, we are going to define the class of each variable in the data, retaining only the variables relevant to the analysis. 
It should be noted that the data-set below has still retained all fungicide active ingredients. 
Before dropping the non-DMI fungicides from the final meta-analysis we will inspect their influence on grain yield.
